Assessing the Replicability of Psychological Science Through Pedagogy

### 2016-07-01 paper/paper.Rmd

```{r global_options, include=FALSE}
rm(list=ls())
library(knitr)
knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = FALSE, 
                      fig.path='figs/', echo=FALSE, warning = FALSE, 
                      cache=TRUE, message = FALSE, sanitize = TRUE)
library(dplyr)
library(xtable)
library(readr)
library(ggplot2)
```

@@

```{r, results='asis'}
setwd("~/replication_project")
project_plan_raw <- read_csv("data/planning_and_outcomes.csv")

@@

results <- read_csv("data/all_project_info.csv")

d <- left_join(project_plan, results)
```

>>>>

```{r global_options, include=FALSE}
rm(list=ls())
library(knitr)
knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = FALSE, 
                      fig.path='figs/', echo=FALSE, warning = FALSE, 
                      cache=TRUE, message = FALSE, sanitize = TRUE)
library(readr)
library(dplyr)
library(xtable)
library(readr)
library(ggplot2)
```

@@

```{r, results='asis'}
project_plan_raw <- read_csv("data/planning_and_outcomes.csv")

@@

project_data_summary <- read_csv("data/project_data_summary.csv")

d <- left_join(project_plan, project_data_summary)
```
